\chapter{Threats To Validity}\label{sec:threats}

%\todo{Report about each type of threat to the validity of the experiment, %according to the classification framework proposed by Wohlin \etal %\cite{wohlin12}.
%https://link-springer-com.vu-nl.idm.oclc.org/content/pdf/10.1007%2F978-3-642-29044-2.pdf
%}

\section{Internal Validity}
This research provides a set of architectural significant requirements, tactics and patterns. Combined with an interpretation when to use these tactics and patterns.
This set can be considered as a starting point and viable selection. However, it will not rule out these tactics and patterns are already in place or other tactics and patterns are better suitable in some situations. If the interviews would be conducted with different subjects in other government organisations it can be assumed the set of variables will be extended or even considered inexhaustible. 
%\todo{Internal validity: This aspect of validity is of concern when causal relations are examined. When the researcher is investigating whether one factor affects an investigated factor there is a risk that the investigated factor is also affected by a third factor. If the researcher is not aware of the third factor and/or does not know to what extent it affects the investigated factor, there is a threat to internal validity}

\section{External Validity}
This quantitative research is based on a limited amount of interviews. A restricted amount of time and available resources resulted in a limited sample of selected subjects. The outcomes of the interviews can be considered as a pilot. A starting point for further research and actions within the organisation. 
However, the subjects of these interviews are experts in the domain of personal identity. The domain expert, information analyst  are a source of truth for the Dutch government as a whole. When there is a question on the design and content of the identity system, they are the liaison for different ministries and government departments. The directing architect is involved as peer reviewer for government standards. All subjects have more than 10 years experience at the National office for identity data.  

%\todo{External validity: This aspect of validity is concerned with to what extent it is possible to generalize the findings, and to what extent the findings are of interest to other people outside the investigated case. During analysis of external validity, the researcher tries to analyze to what extent the findings are of relevance for other cases. In case studies, there is no population from which a statistically representative sample has been drawn. However, for case studies, the intention is to enable analytical generalization where the results are extended to cases which have common characteristics and hence for which the findings are relevant, i.e. defining a theory.}

\section{Construct Validity}
Within this qualitative research semi-structured interviews are used to collect data. Firstly, this method is chosen because the subjects are experts in their fields of expertise, namely personal identity. Limiting them to a questionnaire or structured interview would not provide unexpected and new information or insights in their field of expertise. Secondly, the use data gathering techniques like unstructured interviews could result in an unlimited stream of information and history. Blandford \etal \cite{Blandford2016QualitativeHR} define that semi-structured interviews “inevitably bring in the interests of the researcher as well as the participant.”. 
\par
It’s needed to acknowledge the bias introduced by the researcher. Blandford \etal \cite{Blandford2016QualitativeHR} define the shaping of data gathering by a researcher as follows: “The researcher is shaping the conversation and the data that is gathered, and the extent of that shaping should be recognized and reported transparently and unapologetically.” The relationship between researcher and subjects is as colleagues within a Dutch government body.
\section{Reliability}
The amount of interviewees and other participants can be considered low. However, the participants are specialists in their field of expertise in maintaining systems of personal data for the Dutch government. Executing this research in other settings, for example commercial parties or a different government body, could deliver different outcomes.
The implementation sections covers one pattern and a set tactics. It can be argued there is a more extensive set of patterns and tactics that can be applied.

%\todo{Voorbeeld:The main threats to the internal validity are: learning effect, subjects’ %experience,
%information exchange among participants, author’s bias, author influence, the order of
%methods in the training and understandability of the documents. Two experimental
%objects were used to deal with the learning effect, such as ensuring that each subject
%applied each method in a different system and considering all the possible
%combinations of both the method order and the experimental objects. There were no
%differences on the subjects’ experience since none of them had experience in
%architecture evaluations. The subjects were introduced to the tasks and the problems
%they would have to solve via their participation in training sessions on both methods.
%Information exchange was alleviated by using different experimental objects at the
%same time, and monitoring the subjects while they performed the tasks. Since the
%experiment was designed to take place in two sessions, the subjects might have been
%able to exchange information during the time between the sessions, but this was
%alleviated by asking the participants to return the material at the end of each session.
%The author’s bias in this experiment may have influenced the results since the training
%sessions were conducted by an author of the method. The author influence was
%alleviated by not disclosing to the subjects the authorship of the QuaDAI method. The
%order of methods during the training and experimental sessions could have also
%influenced the results since it was the same in each session. This issue will be
%investigated in future replications of this experiment. The understandability of the
%material was alleviated by clearing up all the misunderstandings that appeared in the
%pilot experiment and experimental sessions.
%The main threat to external validity is the representativeness of the results. The
%representativeness of the results might be affected by the evaluation design and the
%participant context selected. The evaluation design might have had an impact on the
%results owing to the kind of architectural models and quality attributes to be
%evaluated. We selected two different architectures, from two different domains, two
%different NFRs and four different patterns for each experimental object. The
%experiment was conducted with students with no experience in architectural
%evaluations, and who received only limited training on the evaluation methods.
%However, since they were final year students they can be considered as novice users
%of architectural evaluation methods, and the next generation of practitioners [24]. The
%results could thus be considered as representative of novice evaluators.
%The main threats to the construct validity are the measures used to quantify the
%dependent variables. Effectiveness was measured using the Euclidean distance which
%has commonly been used to measure the goodness of a solution with regard to a set of
%opposed NFRs with different purposes [12] [33]. The subjective variables are based
%on the Technology Acceptance Method (TAM) [13], a well-known and empirically
%validated model for the evaluation of information technologies. The reliability of the
%questionnaire was tested by applying the Cronbach test. Questions related to PEOU,
%PU and ITU obtained a Cronbach’s alpha of 0.824, 0.870 and 0.831, which is higher
%than the acceptable minimum (0.70) [27]. The main threat to the conclusion validity
%is the validity of the statistical tests applied. This threat was alleviated by applying a }