
% Thesis Abstract -----------------------------------------------------


%\begin{abstractslong}    %uncommenting this line, gives a different abstract heading
\begin{abstracts}        %this creates the heading for the abstract page

\noindent \textit{Context}. 
Privacy of citizens is protected by law. However, leakage of citizens' data occurs more often and possibly has negative impact on the lives of these citizens.

\noindent \textit{Goal}. 
Goal of this research is to provide an overview of the domain of identity theft and to provide a definition of concrete problems together with possible solutions.

\noindent \textit{Method}. 
Research has been executed based on literature study and an experiment of semi-structured interviews with experts in the field of identity data within the Dutch government. 
Coding is used to extract information from the semi-structured interviews. Reproduction package can be found on Github \url{https://github.com/mswaap1985/Master-thesis}.

\noindent \textit{Results}. 
Using the method of coding raw output is converged into Business Goals and Concerns which resulted in Architecturally Significant requirements that could be taken in consideration mitigating privacy risks when designing or evaluating software systems.

\noindent \textit{Conclusions}. 
The domain of Identity fraud was scoped down to identify operational problems that can be mitigated. The overview and implementation section of this research contain Architecturally Significant Requirements (ASR). Together with practical use-cases as an example these ASRs facilitate in selecting and evaluating an appropriate software solution. 

\end{abstracts}
%\end{abstractlongs}


% ---------------------------------------------------------------------- 
